\documentclass[draft]{article}

% - Style
\usepackage{base}

% - Title
\gdef\theassessment{PHYS4001 - Literature Review}
\gdef\thesupervisor{Professor Igor Bray}
\gdef\theinstitution{Curtin University}
\gdef\thestudentid{1834 2884}

\title{Ionization Amplitudes in Electron-Helium Collisions within the S-Wave
  Model}
\author{Tom Ross - \thestudentid}
\date{\today}

% - Headers
\pagestyle{fancy}
\fancyhf{}
\rhead{\theauthor}
\chead{}
\lhead{\theassessment}
\rfoot{\thepage}
\cfoot{}
\lfoot{}

% document

\begin{document}

% cover page

\begin{titlepage}
  {
    \centering
    {
      \scshape\large\theinstitution
      ~\\
      \scshape\large\theassessment
      \par
    }
    \vspace{1 em}
    \hrule
    ~\\
    {
      \scshape\huge\thetitle
      \par
    }
    \vspace{1 em}
    {
      \scshape\large
      {
        \theauthor
        ~\\
        \thesupervisor
      }
      \par
    }
    ~\\
    \hrule
  }
  \vspace{2 em}
  {
    [ABSTRACT]
  }
\end{titlepage}

\clearpage

% contents page

\tableofcontents
\listoffigures

\listoftables

% statement

\clearpage

\section{Introduction}
\label{sec:introduction}

\section{Theory}
\label{sec:theory}

\subsection{Convergent Close-Coupling Method}
\label{sec:ccc-method}

\subsubsection{Electron-Helium Hamiltonian}
\label{sec:electron-helium-hamiltonian}

Laguerre basis.

Implications of spin / Pauli exclusion principle.

Target structure.

\subsubsection{Close-Coupling Equations}
\label{sec:cc-equations}

Description of CC equations.

\subsection{Ionization Amplitudes}
\label{sec:ionization-amplitudes}

Transition amplitudes - discrete excitation.

Discuss auto-ionization (auto-ionization from excited states)?

Ionization amplitudes.

Limitation of ionization amplitudes to pseudostate energies in (CCC), and
resulting method for calculating ionization amplitudes.

Behaviour of ionization amplitudes for Singlet states.

Singly-Differential-Cross-Section for electron-impact Ionization.

\subsection{Ionization from Ansatz of Zatsarinny and Bartschat}
\label{sec:ansatz-zatsarinny-bartschat}

\subsection{Ionization from Exterior Complex Scaling}
\label{sec:ionization-ecs}

\section{Survey of Current Literature}
\label{sec:survey-literature}

\subsection{Extant Ionization Calculations with Close Coupling-Method}

\subsection{Ionization Calculations with Ansatz of Zatsarinny and Bartschat}

\subsection{Ionization Calculations with Exterior Complex Scaling}

\section{Questions}

SDCS?

Re-scaling?

Ionization vs Ionisation?

Frozen-core model?

e-He or e-(He+)?

\section{Conclusion}
\label{sec:conclusion}

\clearpage

\bibliographystyle{chicago}
\bibliography{references}

\end{document}